Are rankings of financial analysts useful for investors?

### 2015-02-14 doc/paper/paper-knitr.tex
Initial commit

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
%\usepackage{natbib}
\usepackage[natbibapa]{apacite}

@@

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\begin{document}

<<include=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

<<load.data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
library(reshape2)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
load('cache/q.data.RData')
load('cache/final.bl.RData')
load('cache/market.set.RData')
load('cache/example.dt.RData')
source('lib/BL-functions.R')
#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
split.rank <- function(r,n){
if(max(r,na.rm=T)==3|max(r,na.rm=T)==4){n=1}else{if(max(r,na.rm=T)==5|max(r,na.rm=T)==6){n=2}else{if(max(r,na.rm=T)==7|max(r,na.rm=T)==8){n=3}}}#else{if(max(r,na.rm=T)==9|max(r,na.rm=T)==10){n=4}}}}        
        t <- head(r,n)
        b <- tail(r,n)
        replace(replace(replace(replace(r,t,'top'),b,'bottom'),setdiff(r,c(t,b)),'middle'),which(is.na(r)),'noRank')
}

summary.stat <- function(dt){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,.N,by=year],dt[,.N,by=list(year,Broker)][,.N,by=year][,N],dt[,.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,.N],'Brokers'=dt[,.N,by=Broker][,.N],'Observations'=prettyNum(dt[,.N],big.mark=' '))))
}

summary.mean.stat <- function(dt,value){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,descriptive.f(N),by=year][V1==value][,c(1,3),with=F],dt[,.N,by=list(year,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F],dt[,.N,by=list(year,Stock,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F]),c('Years','Firms','Brokers','Observations')),setnames(data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,descriptive.f(N)][V1==value][,2,with=F],'Brokers'=dt[,.N,by=Broker][,descriptive.f(N)][V1==value][,2,with=F],'Observations'=dt[,.N,by=list(Stock,Broker)][,descriptive.f(N)][V1==value][,2,with=F])),c('Years','Firms','Brokers','Observations')))
}

trunk.percent <- 0.05
stocks <- unique(market.set[,Stock])
#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)

q.data <- na.omit(q.data.full[stocks])
q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])

### General stat of TP/P-1
stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')

core.dt <- unique(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],by=c('q.id','Broker','Stock'))
quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])

n <- 3
ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]

#core.dt[Stock=='AAPL'&Broker=='PIPER'][,list(q.id,rank)][,NextPeriod:=split.rank(rank,5),by=q.id][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))]][]

require(descr)
ranked.pt.dt$CurrentPeriod <- factor(ranked.pt.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
ranked.pt.dt$NextPeriod <- factor(ranked.pt.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
cont.tab <- ranked.pt.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.c=T,prop.t=T,prop.chisq = F,plot=F)]

###Statistics for views:
###non rank base data
load('cache/nr.views.RData')
load('cache/pt.rank.views.RData')
load('cache/eps.rank.views.RData')

load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')

complete.dt <- rbindlist(lapply(43:85,function(q){ complete.dt[q.id==q]}))
eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')

quarters.eps <- data.table(q.id=complete.dt[order(q.id)][,unique(q.id)])

ranked.eps.dt <- complete.dt[,merge(setkey(quarters.eps,q.id),.SD,all=T,allow.cartesian=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]

ranked.eps.dt$CurrentPeriod <- factor(ranked.eps.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
ranked.eps.dt$NextPeriod <- factor(ranked.eps.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))

eps.cont.tab <- ranked.eps.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.t=T,prop.c=T,prop.chisq = F,plot=F)]
#brok.full.stat.pt <- acast(setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
#pt.full.period <- setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view)],c('Statistics','value'))

brok.full.stat.pt <- acast(setnames(na.omit(setkey(core.dt,Stock)[,.N,by=list(Stock,q.id,year)])[,descriptive.f(N),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
pt.full.period <- setnames(setkey(core.dt,Stock)[,.N,by=list(Stock,q.id,year)][,descriptive.f(N)],c('Statistics','value'))
#Views stat
stat.rank.views <- acast(setnames(pt.rank.views[,descriptive.f(View),by=list(year,Method)],c('Year','Method','Statistics','value')),Year~Method~Statistics,value.var='value')
rank.views.full.period <- acast(setnames(pt.rank.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')

pt.eps.stat.rank.views <- acast(setnames(eps.rank.views[,descriptive.f(View),by=list(year,Method)],c('Year','Method','Statistics','value')),Year~Method~Statistics,value.var='value')

pt.eps.rank.views.full.period <- acast(setnames(eps.rank.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')

stat.nr.views <- acast(setnames(nr.views[Method=='true',descriptive.f(View),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
nr.full.period <- acast(setnames(nr.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')

#setkey(pt.rank.views,Stock,q.id,year)
#setkey(nr.views,Stock,q.id,year)

brok.full.stat.eps <- acast(setnames(na.omit(setkey(complete.dt,Stock)[,.N,by=list(Stock,q.id,year)])[,descriptive.f(N),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
eps.full.period <- setnames(setkey(complete.dt,Stock)[,.N,by=list(Stock,q.id,year)][,descriptive.f(N)],c('Statistics','value'))

#join.dt <- na.omit(setkey(core.dt,q.id,Broker,Stock,Sector)[setkey(complete.dt,q.id,Broker,Stock,Sector)])

load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
#num.b <- apply(estimates[,working.s,working.b,2],c(1,3),function(i){length(i[!is.na(i)])})
#num.s <- apply(estimates[,working.s,working.b,2],c(1,2),function(i){length(i[!is.na(i)])})
#final.bl <- setkey(all.final.bl,Method)[methods]
#methods <- as.character(unique(final.bl$Method)[c(1:7,11:13)])
final.bl <- final.bl[,Method:=ifelse(Method=='true',strategies[1],ifelse(Method=='naive',strategies[2],strategies[3]))]

final.bl$Method <- factor(final.bl$Method,levels=strategies)
final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
final.bl <- final.bl[,ann.ret:=ann.ret*100]
bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Aggregation','Views'),measure.vars  = c('ann.ret','ann.sd','ann.sr','meanViews','Ave.TO')),by=c('Method','Aggregation','variable','Views')),Views~Method~Aggregation~variable,value.var = 'value')
@

@@

The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person.} in TP dataset is \Sexpr{q.data[!is.na(trunk.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(trunk.view),.N,by=Stock][,.N]} S\&P500 stocks. Given the fact that financial analyst mostly issue TP annually,\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have 12-month horizon \citep{glushkov2009}} we assume that an analyst keeps her TP forecast valid for one calendar year until it gets revised or expires after one year.

Consistent with other studies on analysts' expected returns based on price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}). This is done due to the extreme values cause by misalignment errors found on I/B/E/S data.\footnote{We found some differences in the databases as there can the cases when one of the databases did not performed the stock-splits or dividend payment adjustment.} The final sample size of $TP/P-1$ observations is reduced from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. To implement the ranking, we require that a stock had at least three brokers per quarter that issue EPS forecasts. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Finally, we consider only S\&P500 stocks. All these requirements reduce our sample of EPS forecasts to \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks. The total number of EPS-Stock-Broker observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
Panel A shows the composition of each category for rankings based on the accuracy in target prices. We observe that the distribution of the $top_{t}$ group is as follows: \Sexpr{round(cont.tab[[3]][1,1],3)*100}\%  of analysts stay at the same ranking category from the $top_{t-1}$; \Sexpr{round(cont.tab[[3]][2,1],3)*100}\% move from the $middle_{t-1}$; \Sexpr{round(cont.tab[[3]][3,1],3)*100}\% from the $bottom_{t-1}$; and \Sexpr{round(cont.tab[[3]][4,1],3)*100}\%  from the $noRank_{t-1}$. It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank. Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (\Sexpr{round(cont.tab[[3]][4,4],3)*100}\%). This suggests that analysts are not frequent in issuing target price reports.

Table (\ref{tab:ret-stat}) provides descriptive statistics of target price and EPS data. Panel A shows the number of target prices per stock per quarter. For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations with average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} target price reports per quarter per stock. Panel B of the table presents the statistics of the number of EPS forecasts. In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} forecast-quarter observations. The average number of forecasts per stock per quarter is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.

We applied the ranking procedure outline in section \ref{def-q} on both datasets. For target price rankings, we use the average per quarter daily errors as the measure of analysts' forecasting ability (\ref{tp:pmafe}). The daily frequency allows us to capture the analysts' performance with better precision. Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices. As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock. At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts. Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices. The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4). In this example, LEGG is the most accurate in forecasting the AMZN stock and DLJ is the least.
\subsection{Ranking contingency analysis}
The rankings allows us to perform a contingency analysis of analysts' ranks and their intetemporal changes. Table (\ref{tab:rank-stat}) demonstrates the results. For this table, we split rankings into four categories: the analysts fall into \emph{top} category if they have ranks below or equal to \Sexpr{n},\footnote{The choice comes from the restriction of a stock having at least \Sexpr{n} brokers of coverage in a quarter.} the \emph{bottom} category includes analysts whose ranks fall into the last \Sexpr{n} ranks, the \emph{middle} category is for analysts who neither \emph{top} nor \emph{bottom}, and if analysts do not issue any report they fall into the \emph{noRank} category.  We, then, calculate a distribution of analysts for each of the category for the period $t$,i.e., for a given ranking group, we would like to know how it was composed.

%This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
%An interesting observation is for the \emph{noRank} category: \Sexpr{ round(cont.tab[[2]][4,1],3)*100}\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.

Panel B depicts the similar analysis for the EPS forecast rankings. For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$. However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes \Sexpr{round(eps.cont.tab[[3]][4,1],3)*100}\%, for the \emph{middle} --- \Sexpr{round(eps.cont.tab[[3]][4,2],3)*100}\%, and for the \emph{bottom} --- \Sexpr{round(eps.cont.tab[[3]][4,3],3)*100}\%. This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.

@@

We present descriptive statistics of the expected stock returns in table (\ref{tab:view-stat}). Panel A show the statistics for $consQ$ defined in eq. (\ref{consq}). The consensus among the analysts about stock expected return is \Sexpr{round(nr.views[,mean(View,na.rm=T),by=Method][Method=='true',V1],3)*100 }\%.  Panel B of the table shows the statistics for $rankQ$ obtained from the rankings based on the target price accuracy. We observe a reduction in average per stock expected return with the mean of \Sexpr{ round(rank.views.full.period['true','mean'],3)*100}\%. The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of \Sexpr{ round(pt.eps.rank.views.full.period['true','mean'],3)*100}\%. Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.

@@

\subsection{Passive strategy}
Panel A shows  the performance of the passive strategy \textit{Market}. The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,'ma',1],2)}\% and an annualized Sharpe ratio (SR) of \Sexpr{ round(bl.results['Market',1,'ma','ann.sr'],3)}. The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'ma','meanViews'])} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'ma','Ave.TO'],3)}, which demonstrates the ins/outs of the S\&P 500 constituents list.

\subsection{Results of the perfect ranking foresight strategy}
Panel B presents the result for the case of \tr{} information availability set. The annualized cumulative returns for each of the active strategies (CONS,TP,and EPS) are: CONS =\Sexpr{round(bl.results['CONS',1,'ma',1],2)}\%, TP = \Sexpr{round(bl.results['TP',1,'ma',1],2)}\%, and EPS = \Sexpr{round(bl.results['EPS',1,'ma',1],2)}\%. All the strategies outperform the benchmark. The result confirms that these strategies set an upper bound for the cumulative return yield. It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.

@@

\subsection{Results of feasible strategies}
Panels C and D of the table (\ref{tab:strategy}) show the trading results of the feasible information availability sets. In the case of the \naive{}, the strategy that outperforms all the others (including the \emph{Market}) is the TP strategy which yields an annualized cumulative return of \Sexpr{round(bl.results['TP',2,'ma',1],2)}\%. The other two strategies (CONS and EPS) resulted in below-the-market performance (annualized cumulative return of \Sexpr{round(bl.results['CONS',2,'ma',1],2)}\% and \Sexpr{round(bl.results['EPS',2,'ma',1],2)}\% respectively). The case of the \default{}, demonstrates the worse results as none of the active strategies is able to outperform the \emph{Market} (TP = \Sexpr{round(bl.results['TP',3,'ma',1],2)}\%, CONS = \Sexpr{round(bl.results['CONS',3,'ma',1],2)}\%, EPS = \Sexpr{round(bl.results['EPS',3,'ma',1],2)}\%)

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
   \multicolumn{6}{l}{\textbf{Panel A: TP}} \\
<<desc-pt,echo=F,results='asis'>>=

data.to.display <- c('nbr.val','min','mean', 'median','max','std.dev')
results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])

options(xtable.comment = FALSE)
cat("Years & Observ & Min& Mean & Median &Max& std.dev\\\\\n")
cat('\\midrule \n')
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(results.final,display=c('s','d','f','f','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
   \multicolumn{6}{l}{\textbf{Panel B: EPS}} \\
<<desc-eps,echo=F,results='asis'>>=

results.final <- rbind(brok.full.stat.eps[,data.to.display],'Total period'=setkey(setnames(setkey(complete.dt[,.N,by=list(Stock,q.id,year)],year)[,descriptive.f(N)],c('Statistics','value')),Statistics)[data.to.display][,value])

print(xtable(results.final,display=c('s','d','f','f','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
@
\bottomrule
\end{tabularx}
\end{table}

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
%\usepackage{natbib}
\usepackage[natbibapa]{apacite}

@@

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person.} in TP dataset is 351, covering 497 S\&P500 stocks. Given the fact that financial analyst mostly issue TP annually,\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have 12-month horizon \citep{glushkov2009}} we assume that an analyst keeps her TP forecast valid for one calendar year until it gets revised or expires after one year.

Consistent with other studies on analysts' expected returns based on price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the 5\textsuperscript{th} percentile (values below \ensuremath{-0.114}) and the 95\textsuperscript{th} percentile (values above 0.791). This is done due to the extreme values cause by misalignment errors found on I/B/E/S data.\footnote{We found some differences in the databases as there can the cases when one of the databases did not performed the stock-splits or dividend payment adjustment.} The final sample size of $TP/P-1$ observations is reduced from 145 628 to 131 066.

The initial file of quarterly EPS forecast consists of  571 brokers covering 3655 stocks. To implement the ranking, we require that a stock had at least three brokers per quarter that issue EPS forecasts. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Finally, we consider only S\&P500 stocks. All these requirements reduce our sample of EPS forecasts to 172 brokers covering 449 stocks. The total number of EPS-Stock-Broker observation is 107 626.
Panel A shows the composition of each category for rankings based on the accuracy in target prices. We observe that the distribution of the $top_{t}$ group is as follows: 14.5\%  of analysts stay at the same ranking category from the $top_{t-1}$; 53.6\% move from the $middle_{t-1}$; 13.1\% from the $bottom_{t-1}$; and 18.8\%  from the $noRank_{t-1}$. It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank. Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (78.4\%). This suggests that analysts are not frequent in issuing target price reports.

Table (\ref{tab:ret-stat}) provides descriptive statistics of target price and EPS data. Panel A shows the number of target prices per stock per quarter. For the sample period (1999-2009), we report 15 079 stock-quarter observations with average of 6.7 target price reports per quarter per stock. Panel B of the table presents the statistics of the number of EPS forecasts. In total, the EPS forecast sample has 14 354 forecast-quarter observations. The average number of forecasts per stock per quarter is 7.5.

We applied the ranking procedure outline in section \ref{def-q} on both datasets. For target price rankings, we use the average per quarter daily errors as the measure of analysts' forecasting ability (\ref{tp:pmafe}). The daily frequency allows us to capture the analysts' performance with better precision. Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices. As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock. At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts. Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices. The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4). In this example, LEGG is the most accurate in forecasting the AMZN stock and DLJ is the least.
\subsection{Ranking contingency analysis}
The rankings allows us to perform a contingency analysis of analysts' ranks and their intetemporal changes. Table (\ref{tab:rank-stat}) demonstrates the results. For this table, we split rankings into four categories: the analysts fall into \emph{top} category if they have ranks below or equal to 3,\footnote{The choice comes from the restriction of a stock having at least 3 brokers of coverage in a quarter.} the \emph{bottom} category includes analysts whose ranks fall into the last 3 ranks, the \emph{middle} category is for analysts who neither \emph{top} nor \emph{bottom}, and if analysts do not issue any report they fall into the \emph{noRank} category.  We, then, calculate a distribution of analysts for each of the category for the period $t$,i.e., for a given ranking group, we would like to know how it was composed.

%This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
%An interesting observation is for the \emph{noRank} category:  round(cont.tab[[2]][4,1],3)*100\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.

Panel B depicts the similar analysis for the EPS forecast rankings. For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$. However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes 34.3\%, for the \emph{middle} --- 43.9\%, and for the \emph{bottom} --- 48.7\%. This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.

@@

We present descriptive statistics of the expected stock returns in table (\ref{tab:view-stat}). Panel A show the statistics for $consQ$ defined in eq. (\ref{consq}). The consensus among the analysts about stock expected return is 20.1\%.  Panel B of the table shows the statistics for $rankQ$ obtained from the rankings based on the target price accuracy. We observe a reduction in average per stock expected return with the mean of 15.4\%. The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of 11.2\%. Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.

@@

\subsection{Passive strategy}
Panel A shows  the performance of the passive strategy \textit{Market}. The strategy resulted in an annualized cumulative return of 4.49\% and an annualized Sharpe ratio (SR) of 0.278. The average number of stocks used per quarter is 499 and the turnover ratio of strategy is 0.003, which demonstrates the ins/outs of the S\&P 500 constituents list.

\subsection{Results of the perfect ranking foresight strategy}
Panel B presents the result for the case of \tr{} information availability set. The annualized cumulative returns for each of the active strategies (CONS,TP,and EPS) are: CONS =5.61\%, TP = 8.2\%, and EPS = 4.93\%. All the strategies outperform the benchmark. The result confirms that these strategies set an upper bound for the cumulative return yield. It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.

@@

\subsection{Results of feasible strategies}
Panels C and D of the table (\ref{tab:strategy}) show the trading results of the feasible information availability sets. In the case of the \naive{}, the strategy that outperforms all the others (including the \emph{Market}) is the TP strategy which yields an annualized cumulative return of 5.46\%. The other two strategies (CONS and EPS) resulted in below-the-market performance (annualized cumulative return of 4.36\% and 2.04\% respectively). The case of the \default{}, demonstrates the worse results as none of the active strategies is able to outperform the \emph{Market} (TP = 4.08\%, CONS = 4.4\%, EPS = 2.32\%)

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
   \multicolumn{6}{l}{\textbf{Panel A: TP}} \\
Years & Observ & Min& Mean & Median &Max& std.dev\\
\midrule 
 1999 & 304 & 3.00 & 4.29 & 4.00 & 11.00 & 1.66 \\ 
  2000 & 1 021 & 3.00 & 4.87 & 4.00 & 14.00 & 2.01 \\ 
  2001 & 1 202 & 3.00 & 5.54 & 5.00 & 16.00 & 2.45 \\ 
  2002 & 1 426 & 3.00 & 6.41 & 6.00 & 19.00 & 3.11 \\ 
  2003 & 1 509 & 3.00 & 7.00 & 6.00 & 21.00 & 3.53 \\ 
  2004 & 1 559 & 3.00 & 7.46 & 7.00 & 22.00 & 3.67 \\ 
  2005 & 1 643 & 3.00 & 7.65 & 7.00 & 24.00 & 3.74 \\ 
  2006 & 1 663 & 3.00 & 7.73 & 7.00 & 22.00 & 3.57 \\ 
  2007 & 1 710 & 3.00 & 7.39 & 7.00 & 22.00 & 3.50 \\ 
  2008 & 1 653 & 3.00 & 6.71 & 6.00 & 18.00 & 3.02 \\ 
  2009 & 1 389 & 3.00 & 5.51 & 5.00 & 19.00 & 2.41 \\ 
   \midrule 
Total period & 15 079 & 3.00 & 6.70 & 6.00 & 24.00 & 3.34 \\
